% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{natbib}
\usepackage[top=1.25in,bottom=1.25in,left=1in,right=1in]{geometry}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\author{}
\date{}

\begin{document}

\hypertarget{template-readme-and-guidance}{%
\section{README: The Elasticity of Aggregate Output with Respect to Capital and Labor}\label{template-readme-and-guidance}}

\hypertarget{overview}{%
\subsection{Overview}\label{overview}}

The code and data in this package uses primarily data from the BEA, along with supplemental data from the BLS, Federal Reserve, NBER, and \cite{dleu2020}. The code is entirely in Stata. One master file runs all the code to clean, organize, and analyze the data for all figures and tables in the paper and appendix. The code takes approximately 15-60 minutes to run depending on machine. 

\hypertarget{data-availability-and-provenance-statements}{%
\subsection{Data Availability and Provenance
Statements}\label{data-availability-and-provenance-statements}}

\hypertarget{statement-about-rights}{%
\subsubsection{Statement about Rights}\label{statement-about-rights}}

I certify that the author of the manuscript has legitimate access to and permission to use the data used in this manuscript.

\hypertarget{optional-but-recommended-license-for-data}{%
\subsubsection{License for Data}\label{optional-but-recommended-license-for-data}}

The data are licensed under a Creative Commons/CC-BY-NC license. See LICENSE.txt for details.

\hypertarget{summary-of-availability}{%
\subsubsection{Summary of Availability}\label{summary-of-availability}}

All data \textbf{are} publicly available.

\hypertarget{details-on-each-data-source}{%
\subsubsection{Details on each Data
Source}\label{details-on-each-data-source}}

\textbf{Public Data Downloads:}
\begin{longtable}{p{4.5in}p{1in}p{1in}}
File & Location & Provided \\
\midrule \\
\multicolumn{3}{l}{Historical Multi-factor Productivity, \cite{blsdata}} \\ \midrule
BLS\_mfp\_historical.csv & Data/USA & TRUE \\
\\ 
\multicolumn{3}{l}{Input-output accounts, \cite{beaio}} \\ \midrule
ImportMatrices\_Before\_Redefinitions\_SUM\_1997-2020.xlsx & Data/USA & TRUE \\
IOMake\_Before\_Redefinitions\_1947-1962\_Summary.xlsx & Data/USA & TRUE \\
IOMake\_Before\_Redefinitions\_1963-1996\_Summary.xlsx & Data/USA & TRUE \\
IOMake\_Before\_Redefinitions\_PRO\_1997-2020\_Summary.xlsx  & Data/USA & TRUE \\
IOUse\_Before\_Redefinitions\_PRO\_1947-1962\_Summary.xlsx  & Data/USA & TRUE \\
IOUse\_Before\_Redefinitions\_PRO\_1963-1996\_Summary.xlsx  & Data/USA & TRUE \\
IOUse\_Before\_Redefinitions\_PRO\_1997-2018\_Summary.xlsx  & Data/USA & TRUE \\
IxI\_TR\_1997-2020\_PRO\_SUM.xlsx & Data/USA & TRUE \\
\\
\multicolumn{3}{l}{Integrated Macroeconomic Accounts, \cite{beaimap}} \\ \midrule
Section1All\_xls.xlsx  & Data/USA & TRUE \\
\\
\multicolumn{3}{l}{Private Fixed Assets by Industry, \cite{beacap}} \\ \midrule
Section3All\_xls.xlsx  & Data/USA & TRUE \\
\\
\multicolumn{3}{l}{Income and Employment by Industry, \cite{beasection6}} \\ \midrule
Section6All\_xls.xlsx  & Data/USA & TRUE \\
\\
\multicolumn{3}{l}{Government Fixed Assets, \cite{beagov}} \\ \midrule
Section7All\_xls.xlsx  & Data/USA & TRUE \\
\\
\multicolumn{3}{l}{Historical Industry Accounts Data, \cite{beahistind}} \\ \midrule
GDPbyInd\_VA\_SIC.xls & Data/USA & TRUE \\
\\
\multicolumn{3}{l}{Utilization-adjusted TFP, \cite{fernalddata}} \\ \midrule
quarterly\_tfp.xlsx & Data/USA & TRUE \\
\\
\multicolumn{3}{l}{Historical Mortgage Rates, \cite{nberhistory}} \\ \midrule
m13045.txt & Data/USA & TRUE \\
m13058.txt & Data/USA & TRUE \\
\\
\multicolumn{3}{l}{Historical S\&P Dividend Yield, \cite{shiller}} \\ \midrule
MULTPL-SP500\_DIV\_YIELD\_MONTH.csv & Data/USA & TRUE \\
\\
\end{longtable}

Data on historical multi-factor productivity was downloaded from the Bureau of Labor Statistics \citep{blsdata} from https://www.bls.gov/productivity/tables/ under ``Historical Total Factor Productivity Measures (SIC 1948-87 linked to NAICS 1987-present)''. A copy of the data is provided in this archive. The data are in the public domain.

Data on input-output accounts was downloaded from the Bureau of Economic Analysis \citep{beaio} from https://www.bea.gov/industry/input-output-accounts-data under ``Use Tables, 1997-2020, 71 Industries'', ``Historical Use Tables/Before Redefinitions/Producer Value, 1963-1996, 65 Industries'', ``Historical Use Tables/Before Redefinitions/Producer Value, 1947-1962, 46 Industries'', and ``Import Tables/Before Redefinitions/Producer Value, 1997-2020''. A copy of the data is provided in this archive. The data are in the public domain.

Data on integrated macroeconomic accounts was downloaded from the Bureau of Economic Analysis \citep{beaimap} from https://www.bea.gov/data/special-topics/integrated-macroeconomic-accounts, selecting ``Begin Using the Data''. Select ``Table S.5.a Nonfinancial Corporate Business'' for download. A copy of the data is provided in this archive. The data are in the public domain.

Data on private fixed assets by industry was downloaded from the Bureau of Economic Analysis \citep{beacap} from https://www.bea.gov/itable/fixed-assets, selecting ``Interactive Data Tables'' and then ``view data in XLS or other formats''. Select ``Section 3 - Private Fixed Assets by Industry'' for download. A copy of the data is provided in this archive. The data are in the public domain.

Data for income and employment by industry was downloaded from the Bureau of Economic Analysis \citep{beasection6} from https://www.bea.gov/itable/national-gdp-and-personal-income, selecting ``Interactive Data Tables'', and then ``view data in XLS or other formats''. Select ``Section 6 - Income and Employment by Industry'' for download. A copy of the data is provided in this archive. The data are in the public domain.

Data for government fixed assets was downloaded from the Bureau of Economic Analysis \citep{beagov} from https://www.bea.gov/itable/fixed-assets, selecting ``Interactive Data Tables'' and then ``view data in XLS or other formats''. Select ``Section 7 - Government Fixed Assets'' for download. A copy of the data is provided in this archive. The data are in the public domain.

Data for historical industry accounts data was downloaded from the Bureau of Economic Analysis \citep{beahistind} from https://www.bea.gov/itable/gdp-by-industry selecting ``Historical 1947-1997 Data'' and then selecting ``Annual Tables'', which will download a zip file. A copy of the data is provided in this archive. The data are in the public domain.

Data for utilization-adjusted TFP \citep{fernalddata} was downloaded from https://www.johnfernald.net/TFP, selecting the ``data\_quarterly\_2020.09.08.xlsx'' file from the drop down list. A copy of the data is provided in this archive. The data are in the public domain.

Data on historical mortgage rates \citep{nberhistory} was downloaded from https://data.nber.org/databases/macrohistory/data/13/, selecting files ``m13045.db'' and ``m13058.db'', which are then saved as text files. A copy of the data is provided in this archive. The data are in the public domain.

Data on S\&P dividend yields \citep{shiller} was downloaded from http://www.econ.yale.edu/~shiller/data.htm, selecting ``U.S. Stock Markets 1871-Present and CAPE Ratio''. A copy of the data is provided in this archive. The data are in the public domain.


\textbf{Public Data Extracts:}
I am using public data that is retrieved by the code using the ``freduse'' package in Stata, which accesses FRED, Federal Reserve Bank of St. Louis, \url{https://fred.stlouisfed.org/series} service. This table contains, by script, a description of the FRED identifier used to make the call, as well as a source of the original data.

\begin{longtable}{p{2in}p{1.5in}p{2.5in}}
Description & Identifier & Citation \\
\midrule
\\
\multicolumn{3}{l}{Code/Elas\_Part1\_AnnInfl.do} \\ \midrule
Non-residential inflation & A009RV1A225NBEA &  \cite{fedint}\\
Residential inflation & A011RV1A225NBEA & \cite{fedint}\\
Equipment inflation & Y033RV1A225NBEA  &  \cite{fedint}\\
IP inflation & Y001RV1A225NBEA  &  \cite{fedint} \\
\\
\multicolumn{3}{l}{Code/Elas\_Part1\_AnnRates.do} \\ \midrule
Prime rate & MPRIME &  \cite{fedint}\\
10-yr Treasury rate & GS10 & \cite{fedint}\\
Corporate AAA rate & AAA  &  \cite{moodys}\\
Corporate BAA rate & BAA  &  \cite{moodys} \\
Three month paper & WCP3M  &  \cite{moodys} \\
Double A paper & DCPN3M  &  \cite{moodys} \\
Federal funds rates & FEDFUNDS  &  \cite{fedint} \\
Corporate profits &  CP & \cite{beaimap} \\
Profits before tax &  A053RC1Q027SBEA & \cite{beaimap} \\
Muni rate &  M13043USM156NNBR & \cite{moodys} \\
30-year mortgage rate &  MORTGAGE30US & \cite{moodys} \\
\end{longtable}

\textbf{Data from replication archives:}
\cite{dleu2020} use Compustat firm-level data to estimate markups at the firm level. They also provide various estimates of elasticities of output with respect to capital at the firm level. Following their replication procedures and code found at \url{https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/5GH8XO}, I extracted industry-level elasticites from their firm-level estimates \citep{dleudata2020}.

As the firm-level data is restricted access my replication package only includes the industry-level summary data from their replication that is publicly available. That file is Data/USA/USA\_DLEU\_theta.csv. 

\textbf{Manual entry data:}
I manually entered data from \cite{taxallow} from https://taxfoundation.org/data /all/federal/oecd-capital-allowances-three-assets-1979-2012 on capital depreciation allowances by capital type for the U.S. The citation includes the URL accessed. The manually entered data are in file Data/USA/capital\_allowances.xlsx

\textbf{Control files:}
The ``data'' for this paper contains several files created by me to perform mappings between different industrial classification systems, and to control the assumptions used in different robustness checks on the results. As these files were created by me I've provided more details on what is in each file. All of these files are included in the replication package.

\textbf{Data/scenarios.csv}: This file lists control parameters for different scenarios used in the code. Each scenario corresponds to a different estimate of the capital elasticity. The fields are used in Code/Elas\_Part3\_Scenarios.do to create the data file used in the estimate for that scenario. The file provided allows for all of the results in the paper to be produced. 

\textbf{Data/USA\_bea\_naics\_map.xlsx}: This file contains multiple tabs which correspond to different mappings of industry codes between sources. A "Notes" tab provides further details. This file is used by the code to assign NAICS industry codes to industry data coming from different sources at the BEA.

\textbf{Data/USA\_sic72\_naics\_map.xlsx}: This file contains the map of SIC 72 industrial codes to NAICs industrial codes. 

\textbf{Data/USA\_sic87\_naics\_map.xlsx}: This file contains the map of SIC 87 industrial codes to NAICs industrial codes. 


\hypertarget{dataset-list}{%
\subsection{Dataset list}\label{dataset-list}}

\begin{longtable}{p{3in}p{1.5in}p{.5in}p{1in}}
\midrule
Data file & Source & Provided & Notes \\
BLS\_mfp\_historical.csv & BLS & TRUE & \\
capital\_allowances.xlsx & Tax Foundation & TRUE & \\
GDPbyInd\_VA\_SIC.xls & BEA & TRUE & \\
ImportMatrices\_Before\_Redefinitions\_SUM\_1997-2020.xlsx & BEA & TRUE & \\
IOMake\_Before\_Redefinitions\_1947-1962\_Summary.xlsx & BEA & TRUE & \\
IOMake\_Before\_Redefinitions\_1963-1996\_Summary.xlsx & BEA & TRUE & \\
IOMake\_Before\_Redefinitions\_PRO\_1997-2020\_Summary.xlsx & BEA & TRUE & \\
IOUse\_Before\_Redefinitions\_PRO\_1947-1962\_Summary.xlsx & BEA & TRUE & \\
IOUse\_Before\_Redefinitions\_PRO\_1963-1996\_Summary.xlsx & BEA & TRUE & \\
IOUse\_Before\_Redefinitions\_PRO\_1997-2018\_Summary.xlsx & BEA & TRUE & \\
IxI\_TR\_1997-2020\_PRO\_SUM.xlsx & BEA & TRUE & \\
m13045.txt & NBER & TRUE & \\
m13058.txt & NBER & TRUE & \\
MULTPL-SP500\_DIV\_YIELD\_MONTH.csv & \cite{shiller} & TRUE & \\
quarterly\_tfp.xlsx & \cite{fernald2014} & TRUE & \\
scenarios.csv & Author & TRUE & Control file \\
Section1All\_xls.xlsx & BEA & TRUE & \\
Section3All\_xls.xlsx & BEA & TRUE & \\
Section6All\_xls.xlsx & BEA & TRUE & \\
Section7All\_xls.xlsx & BEA & TRUE & \\
USA\_bea\_naics\_map.xlsx & Author & TRUE & Control file \\
USA\_DLEU\_theta.csv & \cite{dleu2020} & TRUE & \\
USA\_sic72\_naics\_map.xlsx & Author & TRUE & Control file \\
USA\_sic87\_naics\_map.xlsx & Author & TRUE & Control file \\
\end{longtable}


\hypertarget{computational-requirements}{%
\subsection{Computational
requirements}\label{computational-requirements}}

All code is Stata. Code was last run using Stata 18. Required Stata packages:
\begin{itemize}
  \item \texttt{freduse}. Installed 2023-11-01. Note that your computer needs internet connection to access FRED.
  \item \texttt{binscatter}. Installed 2023-11-01.
\end{itemize}


\hypertarget{software-requirements}{%
\subsubsection{Software Requirements}\label{software-requirements}}

\begin{itemize}
\tightlist
\item
  Stata (code was last run with version 18)

  \begin{itemize}
  \tightlist
  \item
    \texttt{freduse} (as of 2023-11-01)
  \item 
    \texttt{binscatter} (as of 2023-11-01)
  \item
    the program ``\texttt{Elas\_0SETUP.do}'' will ensure required packages are installed
  \item 
    the program ``\texttt{Elas\_MASTER.do}'' will ensure required folders are present
  \end{itemize}
\end{itemize}

Code was run under MacOS 12.12.1


\hypertarget{memory-and-runtime-requirements}{%
\subsubsection{Memory and Runtime
Requirements}\label{memory-and-runtime-requirements}}

Run time is betwen 15-60 minutes depending on machine. Code was last run on a 2020 4-core iMac with M1 chip and 8GB RAM using MacOS 12.12.1. It took approximately 18 minutes to run to completion.

\hypertarget{description-of-programscode}{%
\subsection{Description of
programs/code}\label{description-of-programscode}}

The code is broken down into several larger sections. The scripts in each section are indicated by X in the naming convention Code/Elas\_PartX\_scriptname.do.

\begin{itemize}
  \item Code/Elas\_0SETUP.do ensures required STATA packages are installed. It need only be run once.
  \item Code/Elas\_MASTER.do is, as indicated, the master control script. Executing this will replicate the entire project.
  \item Code/Elas\_Part1\_scriptname.do are scripts that extract data from files or FRED. It produces files that are stored in the CSV directory for use by later scripts. 
  \item Code/Elas\_Part2\_scriptname.do are scripts that do the industry-code matching to data from disparate sources in Part 1. Part 2 produces a single baseline file of data that Part 3 uses to perform estimations.
  \item Code/Elas\_Part3\_scriptname.do are scripts that use the baseline data and estimates the elasticity for each scenario given in the Data/scenarios.csv file. 
  \item Code/Elas\_Part4\_scriptname.do are scripts that use the estimates from Part 3 to produce all tables and figures from the paper and appendix. 
\end{itemize}

Parts 1 and 2 only need to be run one time, and then Part 3 can be run repeatedly on the baseline data produced in those parts. 

If you want to alter the assumptions used in the estimates, or try different combinations of assumptions from what I use in the paper, then you will want to run Parts 1 and 2 once to prepare the data. Then, you should edit the Data/scenarios.csv file to contain the assumptions you want. This file can be edited to be as short as you want (one scenario) or as long as you want. The only requirement is that each scenario have a unique ID number (they need not be consecutive). Part 3 will then use Data/scenarios.csv and run estimates for any scenario you set up. 

Part 4 produces tables and figures for the paper, and as such it assumes that all the scenarios from Data/scenarios.csv in this replication package are available. If you edit Data/scenarios.csv to run new scenarios or drop existing scenarios, those tables/figures will likely not be produced and/or may contain weird results. 

\hypertarget{optional-but-recommended-license-for-code}{%
\subsubsection{License for
Code}\label{optional-but-recommended-license-for-code}}

The code is licensed under a BSD license. See LICENSE.txt included in this repository for details.

\hypertarget{instructions-to-replicators}{%
\subsection{Instructions to
Replicators}\label{instructions-to-replicators}}
\begin{enumerate}
  \item Download the replication package and note the directory into which it was downloaded. There should be two folders downloaded: "Code" and "Data"
  \item Run Code/Elas\_0SETUP.do once to ensure the required packages are installed in Stata.
  \item Edit the "cd" command in Code/Elas\_MASTER.do, line 17, to point towards the directory into which you downloaded the replication.
  \item Excecute Code/Elas\_MASTER.do. It will check for, and create if necessary, other sub-folders required for replication. It will call and execute all other code to replicate the results in the paper.
  \item Check folder "Drafts" for the raw output of figures and tables.
\end{enumerate}


\hypertarget{list-of-tables-and-programs}{%
\subsection{List of tables and
programs}\label{list-of-tables-and-programs}}

The provided code reproduces all tables and figures in the paper and appendix. Of note, Table 1 in the main paper and Table A.1 in the Appendix contain information on data sources and are not produced using any code. 

\subsubsection{Main paper}
\begin{longtable}{p{.75in}p{2.5in}p{2.5in}}
Name & Script & Output file \\ \midrule
Figure 1 & Elas\_Part4\_FigBaseline.do & fig\_cap\_base\_comparison.eps \\
Figure 2 & Elas\_Part4\_FigBaseline.do & fig\_cap\_all\_comparison.eps \\
Figure 3 & Elas\_Part4\_FigRatios.do & fig\_cap\_ratio\_comparison.eps \\
Figure 4 & Elas\_Part4\_FigPrivBus.do & fig\_cap\_priv\_comparison.eps \\
Figure 5 & Elas\_Part4\_FigCapitalType.do (93) & fig\_cap\_combined\_comparison.eps \\
Figure 6 & Elas\_Part4\_FigNoIP.do & fig\_cap\_noip\_comparison.eps \\
Figure 7 & Elas\_Part4\_FigDLEU.do & fig\_cap\_dleu\_comparison.eps \\
Figure 8 & Elas\_Part4\_FigMarkupDLEU.do (52) & fig\_cap\_markupva\_comparison\_dleu.eps \\
Figure 9 & Elas\_Part4\_FigTFP.do (23) & fig\_tfp\_comparison.eps \\
Table 2  & Elas\_Part4\_TabBaseline.do & tab\_scenario\_summary.txt \\
Table 3  & Elas\_Part4\_TabCapitalType.do & tab\_capital\_summary.txt \\
Table 4  & Elas\_Part4\_TabTFP.do  & tab\_tfp\_scenario.txt \\
\midrule
\end{longtable}

\subsubsection{Appendix}
\begin{longtable}{p{.75in}p{2.5in}p{2.5in}}
Name & Script & Output file \\ \midrule
Figure A.1 & Elas\_Part4\_FigPropInc.do & fig\_cap\_prop\_comparison.eps \\
Figure A.2 & Elas\_Part4\_FigMarkCap.do & fig\_cap\_share\_markup\_ind.eps \\
Figure A.3 & Elas\_Part4\_FigMarkCap.do & fig\_cap\_share\_intshare\_ind.eps \\
Figure A.4 & Elas\_Part4\_FigBounds.do & fig\_cap\_bounds\_comparison.eps \\
Figure A.5 & Elas\_Part4\_FigMarkupDLEU.do (39) & fig\_cap\_markupgo\_comparison.eps \\
Figure A.6 & Elas\_Part4\_FigOlleyPakes.do & fig\_cap\_op\_comparison.eps \\
Figure A.7 & Elas\_Part4\_FigBreaks.do & fig\_cap\_break\_comparison.eps \\
Figure A.8 & Elas\_Part4\_FigGovCapital.do & fig\_cap\_govcapital\_comparison.eps \\
Figure A.9 & Elas\_Part4\_FigNegCost.do & fig\_cap\_neg\_comparison.eps \\
Table A.2 & Elas\_Part4\_TabMatch.do (7) & tab\_match\_sic72\_4762part1.txt \\
Table A.3 & Elas\_Part4\_TabMatch.do (9) & tab\_match\_sic72\_4762part2.txt \\
Table A.4 & Elas\_Part4\_TabMatch.do (36)& tab\_match\_sic72\_6386part1.txt \\
Table A.5 & Elas\_Part4\_TabMatch.do (38) & tab\_match\_sic72\_6386part2.txt \\
Table A.6 & Elas\_Part4\_TabMatch.do (66) & tab\_match\_sic87\_8796part1.txt \\
Table A.7 & Elas\_Part4\_TabMatch.do (68) & tab\_match\_sic87\_8796part2.txt \\
Table A.8 & Elas\_Part4\_TabRobust.do (7) & tab\_tr\_summary1.txt \\
Table A.9 & Elas\_Part4\_TabRobust.do (9) & tab\_tr\_summary2.txt \\
Table A.10 & Elas\_Part4\_TabImport.do (7) & tab\_import\_summary1.txt \\
Table A.11 & Elas\_Part4\_TabImport.do (9) & tab\_import\_summary2.txt \\
Table A.12 & Elas\_Part4\_TabCosts.do & tab\_cost\_summary.txt \\
Table A.13 & Elas\_Part4\_TabHouseGov.do & tab\_cost\_hsgov.txt \\
Table A.14 & Elas\_Part4\_TabAnnual.do & tab\_elas\_noprofit\_annual.txt \\
Table A.15 & Elas\_Part4\_TabAnnual.do & tab\_elas\_deprcost\_annual.txt \\
Table A.16 & Elas\_Part4\_TabAnnual.do & tab\_elas\_invcost\_annual.txt \\
Table A.17 & Elas\_Part4\_TabAnnual.do & tab\_elas\_usercost\_annual.txt \\
\midrule
\end{longtable}


\hypertarget{references}{%
\subsection{References}\label{references}}

%\renewcommand{\refname}{\textbf{REFERENCES}}
%\setlength{\bibsep}{1pt}
{\small
\bibliographystyle{aea}
\bibliography{Elasticity.bib}
}



\end{document}
